### 2025-09-12 mixed-models.qmd
20250820 - visualization of mixed models
20250820 - copyediting
20250911 - prevent R chunks in notes from running

@@

```{r}
load(url("https://osf.io/download/q6rjf/"))
```
:::

>>>>

A visualization of mixed models, including the distinction between fixed and random intercepts and slopes, is provided by @Freeman2017: <http://mfviz.com/hierarchical-models> (archived at <https://perma.cc/H2GZ-P5RW>).

@@

load(url("https://osf.io/download/q6rjf/"))
```
:::
